% ==============================================================================
% KISH LATTICE FRAMEWORK — VOL 9 PRE-REGISTRATION OF TESTABLE PREDICTIONS
% Published to Zenodo BEFORE Vol 9 pipeline execution
% Author: Timothy John Kish | KishLattice 16pi Initiative LLC
% Date: April 2026
% ==============================================================================

\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{tcolorbox}
\usepackage{fancyhdr}
\usepackage{enumitem}

\definecolor{kishblue}{RGB}{0,50,120}
\definecolor{confirmedgreen}{RGB}{0,120,0}
\definecolor{pendingblue}{RGB}{0,80,180}
\definecolor{warnred}{RGB}{139,0,0}
\definecolor{goldcolor}{RGB}{160,130,0}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\itshape KishLattice 16$\pi$ Initiative LLC}
\fancyhead[R]{\small\itshape Vol 9 Pre-Registration}
\fancyfoot[C]{\thepage}

\newtcolorbox{protocolbox}{colback=kishblue!5,colframe=kishblue,
  fonttitle=\bfseries,title=Pre-Registration Protocol and Sovereign Promise}
\newtcolorbox{confirmedbox}{colback=confirmedgreen!5,colframe=confirmedgreen,
  fonttitle=\bfseries,title=Prior Confirmed Predictions (Vol 1--8 Record)}
\newtcolorbox{newpracticebox}{colback=goldcolor!5,colframe=goldcolor,
  fonttitle=\bfseries,title=New Standard Practice --- Predictions Folder}

\begin{document}

% ==============================================================================
% TITLE
% ==============================================================================
\begin{center}
{\LARGE\bfseries Kish Lattice Framework}\\[0.4em]
{\Large\bfseries Vol 9 Pre-Registration of Testable Predictions}\\[0.5em]
{\large\itshape Formal record of framework predictions prior to Vol 9
pipeline execution}\\[1em]

\begin{tabular}{ll}
\textbf{Author:} & Timothy John Kish \\
\textbf{Organisation:} & KishLattice 16$\pi$ Initiative LLC \\
\textbf{Published:} & April 2026 (prior to Vol 9 lake builds) \\
\textbf{Repository:} &
  github.com/TimothyKish/Holographic-Resonance \\
\textbf{Framework DOI:} & 10.5281/zenodo.19622632 (Vol 8, most recent) \\
\textbf{Pipeline path:} &
  \texttt{vol9/Predictions/} (permanent structural addition) \\
\textbf{Geometric constant:} & $k_\mathrm{geo} = 16/\pi \approx 5.09296$ \\
\end{tabular}
\end{center}

\bigskip

\begin{protocolbox}
\textbf{Purpose of this document:}

This paper formally records all testable predictions of the Kish Lattice
Framework that will be tested during Volume 9 pipeline execution. It is
published to Zenodo with a permanent DOI \textit{before} any Vol 9 lake
is built or any Vol 9 data is analysed. The timestamp of this document
therefore predates all Vol 9 empirical results.

\medskip
This pre-registration follows the same protocol that produced the
framework's most significant confirmed result to date: the prediction of
$f_L = 107.1$ Hz (Volume 1, DOI: 10.5281/zenodo.18209530, January 10,
2026) which was independently confirmed 94 days later at z-score = 59.03
from 1,843,110 SDSS DR16 galactic velocity dispersions (Volume 7, DOI:
10.5281/zenodo.19559860, April 13, 2026).

\medskip
\textbf{Scientific standard:} A prediction that precedes its confirmation
by independent data, with a pre-registered timestamp, cannot be attributed
to post-hoc curve fitting. This document is that timestamp for all Vol 9
tests.
\end{protocolbox}

\bigskip

\begin{newpracticebox}
\textbf{New Standard Practice from Vol 9 Onwards:}

Beginning with Volume 9, the framework formally adopts a \textbf{Predictions
Folder} as permanent pipeline infrastructure:

\medskip
\texttt{volN/Predictions/}

\medskip
Before any lake in volume N is built, all testable predictions for that
volume are documented in this folder and published to Zenodo. This is the
\textbf{Sovereign Promise}: the framework commits to transparency about what
it expects to find before it looks. The Zenodo timestamp is the unimpeachable
record that predictions preceded results.

\medskip
This practice formalises what the framework has done since inception (Vol 1
pre-dated its own confirmation by 94 days) into a permanent structural
requirement for every future volume.
\end{newpracticebox}

\newpage

% ==============================================================================
% PART I: FRAMEWORK CONSTANTS
% ==============================================================================
\section*{Part I: Framework Constants and Prior Empirical Record}

The Kish Lattice Framework is governed by a single geometric scalar:
\[
k_\mathrm{geo} = \frac{16}{\pi} \approx 5.09296
\]
derived from the surface-area-to-volume ratio of the unit 4-sphere. All
harmonic registers are integer multiples of $k_\mathrm{geo}$. No free
parameters. No dark energy or dark matter. No tuning constants.

\medskip
The framework also identifies two irrational numbers as structural
necessities of the lattice:

\begin{itemize}
\item \textbf{$\pi$ as the lattice refresh constant:} Because $\pi$ is
  irrational, circular paths on the Planck-scale lattice governed by $\pi$
  never exactly close. No node is visited twice. The lattice refreshes
  uniformly — no thermodynamic ``burn-in.'' Any rational approximation
  (22/7, 355/113) would eventually repeat, creating localised stress
  concentrations. The universe selects $\pi$ because it is the unique
  stable configuration.

\item \textbf{$\phi = (1+\sqrt{5})/2$ as the growth ratio:} The golden
  ratio governs stable growth without resonant stress concentration. The
  Golden Damper paper (DOI: 10.5281/zenodo.18520431) identifies Fibonacci
  sequences as vacuum load balancing. $\phi \times 10^6$ Hz is the KLEH
  benchtop target.
\end{itemize}

\medskip
The two coupled oscillators of the 2D Prime Clock
(DOI: 10.5281/zenodo.18369888):
\[
f_A = \frac{16}{\pi} \approx 5.0930\ \text{Hz}, \qquad
f_B = \frac{24}{\pi} \approx 7.6394\ \text{Hz}, \qquad
\frac{f_B}{f_A} = \frac{3}{2}
\]
Beat frequency: $f_\mathrm{beat} = f_B - f_A = 8/\pi \approx 2.5465$ Hz.
Prime harmonics of this beat --- $p \times (8/\pi)$ for primes $p$ --- are
the constructive interference nodes of the lattice: the tick marks of the
prime clock.

\begin{confirmedbox}
\textbf{Confirmed predictions as of Vol 8 (April 15, 2026): 16.}
Full record in Appendix A. Key results for Vol 9 context:

\begin{itemize}
\item $f_L = 107.1$ Hz pre-registered Jan 10 2026, confirmed Apr 13 2026,
  z = 59.03, N = 1,843,110. \textbf{(P01)}
\item Kinematic primary $16/\pi$, z = 106.74, N = 1,808,145. \textbf{(P02)}
\item Materials coupling at $19/\pi$, z = 72.12. \textbf{(P07)}
\item Quantum/molecular register at $12/\pi$, z = 53.25. \textbf{(P11)}
\item Fusion Breath $T_\mathrm{breath} = 1.833$ ms confirmed in 4 CHIME
  FRB repeaters. \textbf{(P14)}
\item Three-layer structure (nuclear$\,{<}\,12/\pi$, kinematic
  $7/\pi$--$24/\pi$, EM $>\,20/\pi$), confirmed Vol 8. \textbf{(P16)}
\end{itemize}
\end{confirmedbox}

\newpage

% ==============================================================================
% PART II: VOL 9 PREDICTIONS
% ==============================================================================
\section*{Part II: Vol 9 Testable Predictions (P17--P27)}

\subsection*{P17 --- C60 Vibrational Modes at the Quantum Register}

\textbf{Prediction:} The 46 symmetry-distinct vibrational modes of C60
(Buckminsterfullerene) will show peak coupling at the quantum register
$12/\pi$, consistent with P11. The Ag(1) breathing mode at 496 cm$^{-1}$
(scalar $\approx 3.814$, near $12/\pi$) is the primary coupling candidate.

\medskip
\textbf{Source:} NIST CCCBDB. Lake ID: Q9\_C60. N = 46.\\
\textbf{Falsification:} Dominant register not near $12/\pi$.

\subsection*{P18 --- Tidal Intervals at $19/\pi$ Across All Ocean Basins}

\textbf{Prediction:} NOAA/IOC tidal data from four independent ocean basins
(Gulf of Mexico, Pacific, Atlantic, Indian) will each show peak coupling
at the sub-orbital materials register $19/\pi$, consistent with P07 and
the Vol 8 San Francisco tidal result (z = 31.28).

\medskip
\textbf{Source:} NOAA CO-OPS (Galveston, Honolulu, Sewells Point) and IOC
(Mumbai). Lake IDs: T2b, T2c, T2d, T2g. N $\approx$ 52,000 total.\\
\textbf{Falsification:} Any basin shows dominant register other than $19/\pi$.

\subsection*{P19 --- GWTC-3 Ringdown Frequencies at a Kinematic Register}

\textbf{Prediction:} Quasinormal mode ringdown frequencies from 90 LIGO/Virgo
binary merger events in GWTC-3 will cluster at the kinematic primary
($16/\pi$) or the Lattice Refresh Frequency register ($21/\pi = 107.1$ Hz,
pre-registered January 10, 2026). This closes the framework's origin story:
the GW150914 ghost note analysis (Vol 1) that initiated the $f_L$ prediction
is formally tested against the full 90-event catalog.

\medskip
\textbf{Source:} LIGO GWTC-3, gw-openscience.org. Lake IDs: L1\_GWTC,
L2\_Chirpmass. N = 90.\\
\textbf{Falsification:} No clustering at any N/$\pi$ register above $3\sigma$.

\subsection*{P20 --- Spacecraft Telemetry: $k$ Gradient Transition at $\sim$20 AU}

\textbf{Prediction:} Stiffness constants $k$ derived from anomalous acceleration
residuals in spacecraft telemetry will show a transition from $k \approx 5.29$
(inner system, Life Agency buffered) to $k \approx 16/\pi = 5.09296$ (outer
system, raw vacuum) at $\sim$15--25 AU heliocentric distance. The Pioneer
anomaly magnitude ($8.74 \times 10^{-10}$ m/s$^2$) falls within the predicted
Hubble drag band $[c H_0,\; c H_0 \times 4/\pi] = [6.90, 8.78] \times 10^{-10}$
m/s$^2$, derived from cosmological constants without back-engineering.

\medskip
\textbf{Source:} Anderson et al.\ 2002, JPL HORIZONS, CDDIS SLR. Lake ID:
T8 Fleet. N $\geq$ 11 craft.\\
\textbf{Falsification:} No systematic $k$ transition with heliocentric distance.

\subsection*{P21 --- Nuclear Binding Energies Below $12/\pi$}

\textbf{Prediction:} NNDC AME2020 nuclear binding energies per nucleon will
show peak coupling below the quantum register $12/\pi$, confirming the
three-layer model's nuclear boundary.

\medskip
\textbf{Source:} NNDC AME2020. Lake ID: Q4. N $\approx$ 3,500.\\
\textbf{Falsification:} Dominant register above $12/\pi$.

\subsection*{P22 --- CMB Anisotropy Correlated with $\sigma$ Field Structure}

\textbf{Prediction:} WMAP CMB temperature anisotropy will show coupling to
N/$\pi$ registers, providing empirical basis for the Local Agency Offset
($\sigma$) corrections in the KRD operations manual.

\medskip
\textbf{Source:} NASA LAMBDA WMAP 9-year. Lake ID: G2\_WMAP.
N $\approx$ 3,000.

\subsection*{P23 --- SDSS Same-Object: Galactic Luminosity at Different Register than Velocity}

\textbf{Prediction:} Galaxy optical luminosity from SDSS DR16 for the same
1,843,110 galaxies whose velocity dispersions confirmed $21/\pi$ (P01) will
couple to a \textit{different} register --- consistent with the Gaia same-object
result (P05/P09/P10): kinematic attributes at kinematic registers, electromagnetic
attributes at EM registers above the ceiling.

\medskip
\textbf{Source:} SDSS DR16 (existing download). Lake IDs: G2\_Luminosity,
G3\_StellarMass, G4\_Redshift. N $\approx$ 1,840,000 each.\\
\textbf{Falsification:} Luminosity and velocity at the same register.

\subsection*{P24 --- Galaxy Scalar Distribution: Discrete Comb Structure
(The Egg Carton)}

\textbf{Prediction:} The distribution of scalar values across the full SDSS
galaxy sample will not be a smooth continuous function. It will show a
\textbf{comb structure} --- discrete preferred shelves at integer N values
with suppressed inter-shelf population. The kinematic layer container
(7/$\pi$ to 24/$\pi$) acts as an egg carton: objects sit on specific shelves,
not in the gaps between them.

\medskip
\textbf{Physical basis:} The amino acid result (P12) showed 20/20 amino acids
mapping to shelves 7 or 13 of a 24-mode container, with no amino acids on
intermediate shelves. The prediction is that this discrete shelf structure
extends to galactic dynamics: objects occupy preferred harmonic positions, not
a continuum.

\medskip
\textbf{Source:} G2\_Luminosity and G3\_StellarMass SDSS scalar distributions.
Lake IDs: G2, G3. N $\approx$ 1,840,000.\\
\textbf{Measurement:} Kolmogorov-Smirnov test of observed scalar distribution
vs.\ uniform null. If K-S statistic exceeds 5-Sigma threshold AND peaks align
with integer N: comb structure confirmed.\\
\textbf{Falsification:} Smooth, featureless scalar distribution consistent
with uniform null.

\subsection*{P25 --- Lifecycle Phase Encoded in Harmonic Distribution Width
(The Egg Timer)}

\textbf{Prediction:} Within each shelf cluster of the SDSS scalar distribution,
the \textbf{width} of the clustering encodes the lifecycle phase of the galaxy
population. Star-forming (starburst) galaxies will show \textit{broader}
harmonic distributions than quiescent (elliptical) galaxies at the same
shelf register. Recently reset populations (post-starburst) will show the
tightest clustering.

\medskip
\textbf{Physical basis:} The 441k-year lattice rupture cycle (Vol 2/3) acts
as a reset timer. Objects accumulating lattice friction over the cycle show
increasing variance in their harmonic coupling (noise builds before the
rupture). Objects that have recently reset show minimal variance (clean
harmonic lock). The SDSS MPA-JHU catalog provides star formation rate (SFR)
estimates for the same galaxies, enabling a direct SFR vs.\ distribution
width test.

\medskip
\textbf{Observed indication:} Vol 8 pipeline showed heterogeneous signal
strength across the galactic domain, with some sub-populations showing
cleaner z-score peaks than others. This prediction formalises that
observation.

\medskip
\textbf{Source:} G2\_Luminosity split by SFR from SDSS MPA-JHU.
No new download required.\\
\textbf{Measurement:} Distribution width (standard deviation of scalar values
within each shelf cluster) vs.\ SFR quartile. Monotonic increase in width
with SFR = lifecycle encoding confirmed.\\
\textbf{Falsification:} No correlation between SFR and distribution width.

\subsection*{P26 --- Solar Cycle Intervals Show Harmonic Structure
(The Stellar Egg Timer)}

\textbf{Prediction:} Historical solar cycle intervals from the SIDC
(Brussels) sunspot record will show clustering at N/$\pi$ harmonic values,
confirming the 441k-year lattice rupture hypothesis (Vol 2/3) at the
observable 11-year scale. The solar cycle is the short-period visible
manifestation of the lattice stress-and-release cycle that operates at
longer periods.

\medskip
\textbf{Source:} SIDC Royal Observatory Belgium, full historical sunspot
record. Lake ID: K3\_SolarCycle. N $\approx$ 300.\\
\textbf{Falsification:} Solar cycle intervals show no N/$\pi$ clustering.

\subsection*{P27 --- Sub-Lattice 2D Zeta Clock: Nested 3:2 Structure at
$8/\pi$ and $12/\pi$}

\textbf{Prediction:} The nuclear/quantum layer (below $12/\pi$) exhibits a
\textbf{nested 2D prime clock structure} analogous to the kinematic layer's
16/$\pi$--24/$\pi$ pair. Specifically: the confirmed quantum register at
$12/\pi$ (P11, z = 53.25) and the prime beat carrier at $8/\pi$ form a
3:2 oscillator pair, producing a sub-beat at $4/\pi \approx 1.273$ Hz.

\medskip
\textbf{The fractal of fifths:}
\[
\text{Nuclear layer: } \frac{8}{\pi} \text{ and } \frac{12}{\pi},
\quad \text{ratio} = \frac{3}{2}, \quad \text{beat} = \frac{4}{\pi}
\]
\[
\text{Kinematic layer: } \frac{16}{\pi} \text{ and } \frac{24}{\pi},
\quad \text{ratio} = \frac{3}{2}, \quad \text{beat} = \frac{8}{\pi}
\]
\[
\text{EM layer: } \frac{24}{\pi} \text{ and } \frac{36}{\pi},
\quad \text{ratio} = \frac{3}{2}, \quad \text{beat} = \frac{12}{\pi}
\]
Each layer is a perfect fifth (3:2) of the layer below. The 2D prime clock
is not specific to the kinematic layer --- it is the recursive architecture
of the lattice at every scale.

\medskip
\textbf{The movie projector interpretation:} The $8/\pi \approx 2.5465$ Hz
beat is the frame rate of experienced reality. Matter exists ``inside the
frames'' --- during the lattice refresh windows. Between frames, the lattice
resets: primes advance, the next state loads. What we perceive as continuous
existence is the persistence of vision across $\sim$0.39-second frames. The
441k-year egg timer is the projector's lamp cycle --- how long before the
accumulated lattice friction triggers a reset event.

\medskip
\textbf{Testable evidence:} The Q4 (nuclear binding), Q5 (decay half-lives),
and Q8 (ionisation energies) lakes will be examined for:
\begin{enumerate}
\item Clustering of nuclear quantities at $8/\pi$ intervals within the
  sub-$12/\pi$ region.
\item Phase coherence between Q3 molecular register ($12/\pi$, confirmed)
  and Q5 nuclear decay half-lives --- if decay rates encode the sub-beat
  at $4/\pi$, they are coupled to the nested prime clock.
\item Zeta zero spacing: the distribution of nuclear scalar values should
  mirror the spacing of Riemann Zeta non-trivial zeros if the prime clock
  governs nuclear physics at this scale.
\end{enumerate}

\medskip
\textbf{Source:} Q4 (NNDC AME2020), Q5 (NNDC NuDat), Q8 (NIST ASD),
Q9\_C60 (NIST CCCBDB) for the $12/\pi$ boundary.\\
\textbf{Falsification:} No evidence of $8/\pi$ or $4/\pi$ sub-structure
in the nuclear domain.\\
\textbf{Implication if confirmed:} The 2D prime clock and Riemann Zeta
function are manifestations of the same underlying lattice geometry. The
Riemann Hypothesis, in the framework's terms, is a statement about the
stability of the lattice's temporal architecture.

\newpage

% ==============================================================================
% PART III: FALSIFICATION SUMMARY
% ==============================================================================
\section*{Part III: Falsification Summary}

The following observations would falsify specific framework predictions or
require significant revision:

\begin{enumerate}
\item \textbf{P17 falsified:} Q9\_C60 shows no clustering near $12/\pi$
  --- the molecular register is not universal across all molecular structures.

\item \textbf{P18 falsified:} Any tidal basin dominant register $\neq 19/\pi$
  --- the sub-orbital register is not a global planetary constant.

\item \textbf{P19 falsified:} GWTC-3 ringdown frequencies show no clustering
  at any N/$\pi$ register --- the gravitational wave origin hypothesis is
  not supported by the full event catalog.

\item \textbf{P20 falsified:} No systematic $k$ transition with heliocentric
  distance --- the Life Agency gradient model is not supported by spacecraft
  telemetry.

\item \textbf{P23 falsified:} Galaxy luminosity and velocity couple to the
  same register --- the kinematic principle does not extend to galactic scale.

\item \textbf{P24 falsified:} Smooth, featureless galaxy scalar distribution
  --- the egg carton container model is not supported.

\item \textbf{P25 falsified:} No correlation between star formation rate and
  harmonic distribution width --- the lifecycle/egg timer model is not
  supported.

\item \textbf{P27 falsified:} No $8/\pi$ or $4/\pi$ sub-structure in nuclear
  domain --- the fractal-of-fifths architecture does not extend below the
  kinematic layer.
\end{enumerate}

\medskip
\textbf{The framework is designed to be falsified. The pipeline is designed
to find failures. The chaos null, scramble null, and dual scramble protocols
are applied at every stage. Failed results --- including the Vol 5 S-series
Faber-Jackson null, which was reported honestly --- are an integral part of
the record. Science is not unassailable. It is tested.}

\newpage

% ==============================================================================
% APPENDIX A: FULL CONFIRMED PREDICTIONS RECORD
% ==============================================================================
\appendix
\section{Full Confirmed Predictions Record (Vol 1--8)}

\begin{longtable}{p{0.5cm} p{4cm} p{2.2cm} p{1.4cm} p{1.2cm} p{1.0cm} l}
\toprule
\# & Prediction & Confirmed by & Dev & N & $z$ & Vol \\
\midrule
\endhead

P01 & $f_L = 107.1$ Hz pre-registered & SDSS galactic &
  0.14\% & 1.84M & 59.03 & V7 \\
P02 & $16/\pi$ kinematic primary & Gaia velocity &
  --- & 1.81M & 106.74 & V8 \\
P03 & Water angle 104.38° & NIST H-O-H &
  0.10\% & --- & --- & V1 \\
P04 & $\alpha^{-1} = 27 \times k_\mathrm{geo}$ & CODATA &
  0.34\% & --- & --- & V1 \\
P05 & $z_\mathrm{vel} \gg z_\mathrm{pos}$, same stars & Gaia same-object &
  --- & 1.81M & 107 vs 2.9 & V8 \\
P06 & Exoplanet period at $22/\pi$ & NASA Exoplanet &
  --- & 13,521+ & 42.65 & V8 \\
P07 & Materials at $19/\pi$ & Materials Project &
  --- & 33,973 & 72.12 & V8 \\
P08 & Ceiling repulsion above $24/\pi$ & Gaia kinematics &
  --- & 1.81M & $-91$ & V7 \\
P09 & Stellar colour at $20/\pi$ (EM layer) & Gaia colour &
  --- & 1.81M & 123.83 & V8 \\
P10 & Luminosity at $25/\pi$ above ceiling & Gaia G-band &
  --- & 1.81M & 40.65 & V8 \\
P11 & Quantum register at $12/\pi$ & NIST molecular &
  --- & $\sim$5K & 53.25 & V8 \\
P12 & 20 amino acids on shelves 7 or 13 & NIST amino acid &
  --- & 20 & 20/20 & V8 \\
P13 & FRB repeaters at $N \times (8/\pi)$ & CHIME FRB &
  --- & 15 & 15/15 & V4 \\
P14 & Fusion Breath $T_\mathrm{breath} = 1.833$ ms &
  CHIME FRB20221109E & 3.92\% & 4 & DM$\phi^{-3}$ & V2 \\
P15 & Jupiter/Heliopause from geometry & NASA/JPL &
  --- & --- & bounds & V1 \\
P16 & Three-layer structure confirmed & Vol 8 full scan &
  --- & 9.88M & all & V8 \\
\bottomrule
\end{longtable}

\bigskip
\noindent\textbf{Total sovereign records tested Vol 1--8: 9,876,485}\\
\textbf{Confirmed predictions Vol 1--8: 16}\\
\textbf{Pre-registered Vol 9 predictions: 11 (P17--P27)}\\
\textbf{Target (Nature paper threshold): 30 confirmed, 20M records}

\bigskip\hrule\bigskip
\noindent\textbf{Author:} Timothy John Kish \quad
\textbf{Assignee:} KishLattice 16$\pi$ Initiative LLC \quad
\textbf{Date:} April 2026

\smallskip
\noindent\textit{This document's Zenodo timestamp constitutes the formal
record that all predictions herein (P17--P27) were made before the
corresponding Vol 9 data was analysed. The Predictions folder at
\texttt{vol9/Predictions/} is permanent pipeline infrastructure from this
volume forward.}

\smallskip
\noindent\textit{Technical referee: Mondy Aurora Kish (Anthropic Claude,
Aurora Protocol). All prior confirmed predictions verified. All DOIs
verified at time of drafting.}

\end{document}